---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BayesIMTR

<!-- badges: start -->

<!-- badges: end -->

The goal of **BayesIMTR** is to identify the potential master transcriptional regulators with the input derived from chromatin accessibility profiling methods(e.g. ATAC-seq, DNase-seq, MNase-seq), the input can be either a file that stores the information of "peaks" generated by common peak-calling algorithms (e.g. MACS2, Homer) or user-defined regions, such as peaks from a differential accessibility analysis(e.g. DiffBind).

## Installation

You can install the development version of BayesIMTR from [GitHub](https://github.com/ZeyuL01/BayesIMTR) with:

```{r}
# install.packages("devtools")
devtools::install_github("ZeyuL01/BayesIMTR")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(BayesIMTR)
library(kableExtra)

##package has three demo knock-out experiment derived datasets c("CTCF","KDM1A","ZBTB7A")
##can take ~10 mins to finish for 1000 rounds.
CTCF_Demo_mat <- Demo(1000,"CTCF")
```

Let's see the results of CTCF demo data.

```{r CTCF}
##Show_Results can summarize the results from Gibbs sampler.
##must specify the burnin
CTCF_Results <- Show_Results(CTCF_Demo_mat,burnin=500)
CTCF_Theta_ij_db <- CTCF_Results[["Theta_ij"]]
CTCF_Theta_i_db <- CTCF_Results[["Theta_i"]]

head(CTCF_Theta_ij_db,10)
```

As we can see, CTCF is ranked into the top 10 TF in the final result.

We may also check the higher level parameters that integrate information from individual ChIP-seq tracks to give one unique rank to each TF.

```{r theta_i}
head(CTCF_Theta_i_db,10)
```

This time CTCF is ranked even higher to the top 1 position over all 1476 TFs.

